method

### 2022-02-08 06_Paper/ER-ED/method.Rmd
added B

# compute posthoc tests for within measures
SubjArousalView_emm <- emmeans::emmeans(SubjArousalView_aov$aov, specs = "block")
#pairs(posthoc_arousalView, adjust = "bonferroni")

@@

# Bayes Factors
SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                           data = Ratings_view,
                                           progress = FALSE)
SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "view_neu"],
                                                                        y = Ratings_view$arousal[Ratings_view$block == "view_neg"]))

@@

arousal_reg = data_ER %>%
  subset(data_ER$block != "view_neu" & data_ER$block != "choice")

aov_arousalReg = afex::aov_ez(data = arousal_reg,
                              id = "ID",
                              dv = "arousal",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)
#afex::nice(aov_arousalReg, es = "pes")

# compute posthoc tests for within measures
posthoc_arousalReg = emmeans::emmeans(aov_arousalReg$aov, specs = "block")
#pairs(posthoc_arousalReg, adjust = "bonferroni")

>>>>

# compute posthoc tests for within measures
SubjArousalView_emm <- emmeans::emmeans(SubjArousalView_aov$aov, specs = "block")

@@

# Bayes Factors
SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                           data = Ratings_view,
                                           progress = FALSE)
SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "view_neu"],
                                                                        y = Ratings_view$arousal[Ratings_view$block == "view_neg"],
                                                                        progress = FALSE, paired = TRUE))$bf

@@

Ratings_reg <- data_ER %>%
  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
Ratings_reg$block <- as.factor(Ratings_reg$block)

SubjArousalReg_aov <- afex::aov_ez(data = arousal_reg,
                              id = "ID",
                              dv = "arousal",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)

# compute posthoc tests for within measures
SubjArousalReg_emm <- emmeans::emmeans(SubjArousalReg_aov$aov, specs = "block")

SubjArousalReg_con <- as.data.frame(pairs(SubjArousalReg_emm, adjust = "bonferroni"))

# Bayes Factors
SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                           data = Ratings_reg,
                                           progress = FALSE)

SubjArousalReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "view_neg"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "distraction"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "view_neg"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "distancing"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "view_neg"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "distraction"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "distancing"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "distraction"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "distancing"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf)
